% ============================================
% ACADEMIC REFERENCES - Research Papers
% ============================================
% This file contains academic paper references for the ATMS project
% Add this section after the open source references

\subsection*{Academic Papers and Research}

\begin{enumerate}[resume]
    \item \textbf{YOLOv8}. G. Jocher, A. Chaurasia, and J. Qiu, "YOLO by Ultralytics," 
    \textit{Ultralytics}, 2023. [Online]. Available: \url{https://github.com/ultralytics/ultralytics}. 
    Based on: J. Redmon et al., "You Only Look Once: Unified, Real-Time Object Detection," 
    \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 
    Las Vegas, NV, USA, 2016, pp. 779-788.
    
    \item \textbf{ByteTrack}. Y. Zhang, P. Sun, Y. Jiang, D. Yu, F. Weng, Z. Yuan, 
    P. Luo, W. Liu, and X. Wang, "ByteTrack: Multi-Object Tracking by Associating Every Detection Box," 
    \textit{European Conference on Computer Vision (ECCV)}, 2022, pp. 1-21. 
    [Online]. Available: \url{https://arxiv.org/abs/2110.06864}.
    
    \item \textbf{Kalman Filter}. R. E. Kalman, "A New Approach to Linear Filtering and Prediction Problems," 
    \textit{Journal of Basic Engineering}, vol. 82, no. 1, pp. 35-45, Mar. 1960. 
    DOI: \url{https://doi.org/10.1115/1.3662552}.
    
    \item \textbf{YOLO (Original)}. J. Redmon, S. Divvala, R. Girshick, and A. Farhadi, 
    "You Only Look Once: Unified, Real-Time Object Detection," 
    \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 
    Las Vegas, NV, USA, 2016, pp. 779-788. DOI: \url{https://doi.org/10.1109/CVPR.2016.91}.
    
    \item \textbf{YOLOv3}. J. Redmon and A. Farhadi, "YOLOv3: An Incremental Improvement," 
    \textit{arXiv preprint arXiv:1804.02767}, 2018. [Online]. Available: 
    \url{https://arxiv.org/abs/1804.02767}.
    
    \item \textbf{YOLOv4}. A. Bochkovskiy, C.-Y. Wang, and H.-Y. M. Liao, "YOLOv4: Optimal Speed and Accuracy of Object Detection," 
    \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, 
    2020, pp. 1446-1453. DOI: \url{https://doi.org/10.1109/CVPR42600.2020.00152}.
    
    \item \textbf{YOLOv5}. G. Jocher, "YOLOv5," \textit{Ultralytics}, 2020. [Online]. 
    Available: \url{https://github.com/ultralytics/yolov5}.
    
    \item \textbf{DeepSORT}. N. Wojke, A. Bewley, and D. Paulus, "Simple Online and Realtime Tracking with a Deep Association Metric," 
    \textit{Proceedings of the IEEE International Conference on Image Processing (ICIP)}, 
    Beijing, China, 2017, pp. 3645-3649. DOI: \url{https://doi.org/10.1109/ICIP.2017.8296962}.
    
    \item \textbf{SORT}. A. Bewley, Z. Ge, L. Ott, F. Ramos, and B. Upcroft, "Simple Online and Realtime Tracking," 
    \textit{Proceedings of the IEEE International Conference on Image Processing (ICIP)}, 
    Phoenix, AZ, USA, 2016, pp. 3464-3468. DOI: \url{https://doi.org/10.1109/ICIP.2016.7533003}.
    
    \item \textbf{Adaptive Traffic Signal Control}. B. Abdulhai, R. Pringle, and G. J. Karakoulas, 
    "Reinforcement Learning for True Adaptive Traffic Signal Control," 
    \textit{Journal of Transportation Engineering}, vol. 129, no. 3, pp. 278-285, May 2003. 
    DOI: \url{https://doi.org/10.1061/(ASCE)0733-947X(2003)129:3(278)}.
    
    \item \textbf{Reinforcement Learning for Traffic Control}. M. Wiering, "Multi-Agent Reinforcement Learning for Traffic Light Control," 
    \textit{Proceedings of the 17th International Conference on Machine Learning (ICML)}, 
    Stanford, CA, USA, 2000, pp. 1151-1158.
    
    \item \textbf{Deep Reinforcement Learning for Traffic Signal Control}. L. Li, Y. Lv, and F.-Y. Wang, 
    "Traffic Signal Timing via Deep Reinforcement Learning," 
    \textit{IEEE/CAA Journal of Automatica Sinica}, vol. 3, no. 3, pp. 247-254, Jul. 2016. 
    DOI: \url{https://doi.org/10.1109/JAS.2016.7508798}.
    
    \item \textbf{Multi-Intersection Traffic Coordination}. S. El-Tantawy, B. Abdulhai, and H. Abdelgawad, 
    "Multiagent Reinforcement Learning for Integrated Network of Adaptive Traffic Signal Controllers (MARLIN-ATSC)," 
    \textit{IEEE Transactions on Intelligent Transportation Systems}, vol. 14, no. 3, pp. 1140-1150, Sep. 2013. 
    DOI: \url{https://doi.org/10.1109/TITS.2013.2255286}.
    
    \item \textbf{Vehicle Speed Estimation}. A. B. Hillel, R. Lerner, D. Levi, and G. Raz, 
    "Recent Progress in Road and Lane Detection: A Survey," 
    \textit{Machine Vision and Applications}, vol. 25, no. 3, pp. 727-745, Apr. 2014. 
    DOI: \url{https://doi.org/10.1007/s00138-011-0404-2}.
    
    \item \textbf{Vehicle Detection and Tracking}. Z. Sun, G. Bebis, and R. Miller, "On-Road Vehicle Detection: A Review," 
    \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 28, no. 5, pp. 694-711, May 2006. 
    DOI: \url{https://doi.org/10.1109/TPAMI.2006.104}.
    
    \item \textbf{Computer Vision for Traffic Analysis}. M. Buch, S. A. Velastin, and J. Orwell, 
    "A Review of Computer Vision Techniques for the Analysis of Urban Traffic," 
    \textit{IEEE Transactions on Intelligent Transportation Systems}, vol. 12, no. 3, pp. 920-939, Sep. 2011. 
    DOI: \url{https://doi.org/10.1109/TITS.2011.2119372}.
    
    \item \textbf{Real-Time Object Detection}. T.-Y. Lin, P. Goyal, R. Girshick, K. He, and P. Dollár, 
    "Focal Loss for Dense Object Detection," \textit{Proceedings of the IEEE International Conference on Computer Vision (ICCV)}, 
    Venice, Italy, 2017, pp. 2980-2988. DOI: \url{https://doi.org/10.1109/ICCV.2017.324}.
    
    \item \textbf{Feature Pyramid Networks}. T.-Y. Lin, P. Dollár, R. Girshick, K. He, B. Hariharan, and S. Belongie, 
    "Feature Pyramid Networks for Object Detection," \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 
    Honolulu, HI, USA, 2017, pp. 2117-2125. DOI: \url{https://doi.org/10.1109/CVPR.2017.106}.
    
    \item \textbf{Vehicle Emission Estimation}. A. Smit, R. Ntziachristos, and P. Boulter, 
    "Validation of Road Vehicle and Traffic Emission Models - A Review and Meta-Analysis," 
    \textit{Atmospheric Environment}, vol. 44, no. 25, pp. 2943-2953, Aug. 2010. 
    DOI: \url{https://doi.org/10.1016/j.atmosenv.2010.05.022}.
    
    \item \textbf{Traffic Flow Prediction}. Y. Lv, Y. Duan, W. Kang, Z. Li, and F.-Y. Wang, 
    "Traffic Flow Prediction with Big Data: A Deep Learning Approach," 
    \textit{IEEE Transactions on Intelligent Transportation Systems}, vol. 16, no. 2, pp. 865-873, Apr. 2015. 
    DOI: \url{https://doi.org/10.1109/TITS.2014.2345663}.
    
    \item \textbf{Anomaly Detection in Traffic}. S. Ma, Y. Zheng, and O. Wolfson, "T-Share: A Large-Scale Dynamic Taxi Ridesharing Service," 
    \textit{Proceedings of the 29th International Conference on Data Engineering (ICDE)}, 
    Brisbane, Australia, 2013, pp. 410-421. DOI: \url{https://doi.org/10.1109/ICDE.2013.6544837}.
    
    \item \textbf{Green Wave Optimization}. D. I. Robertson, "TRANSYT: A Traffic Network Study Tool," 
    \textit{Transport and Road Research Laboratory Report LR 253}, Crowthorne, UK, 1969.
    
    \item \textbf{Intelligent Transportation Systems}. M. Papageorgiou, C. Diakaki, V. Dinopoulou, A. Kotsialos, and Y. Wang, 
    "Review of Road Traffic Control Strategies," \textit{Proceedings of the IEEE}, vol. 91, no. 12, pp. 2043-2067, Dec. 2003. 
    DOI: \url{https://doi.org/10.1109/JPROC.2003.819610}.
    
    \item \textbf{Multi-Object Tracking}. A. Milan, L. Leal-Taixé, I. Reid, S. Roth, and K. Schindler, 
    "MOT16: A Benchmark for Multi-Object Tracking," \textit{arXiv preprint arXiv:1603.00831}, 2016. 
    [Online]. Available: \url{https://arxiv.org/abs/1603.00831}.
    
    \item \textbf{Trajectory Prediction}. A. Alahi, K. Goel, V. Ramanathan, A. Robicquet, L. Fei-Fei, and S. Savarese, 
    "Social LSTM: Human Trajectory Prediction in Crowded Spaces," 
    \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 
    Las Vegas, NV, USA, 2016, pp. 961-971. DOI: \url{https://doi.org/10.1109/CVPR.2016.110}.
    
    \item \textbf{License Plate Recognition}. S. Du, M. Ibrahim, M. Shehata, and W. Badawy, 
    "Automatic License Plate Recognition (ALPR): A State-of-the-Art Review," 
    \textit{IEEE Transactions on Circuits and Systems for Video Technology}, vol. 23, no. 2, pp. 311-325, Feb. 2013. 
    DOI: \url{https://doi.org/10.1109/TCSVT.2012.2203749}.
    
    \item \textbf{Vehicle Classification}. M. Hsieh, Y. Lin, and W. Hsu, "Drone-Based Object Detection by Using Region-Based Fully Convolutional Networks," 
    \textit{Proceedings of the IEEE International Conference on Robotics and Automation (ICRA)}, 
    Singapore, 2017, pp. 6207-6213. DOI: \url{https://doi.org/10.1109/ICRA.2017.7989750}.
    
    \item \textbf{Traffic Congestion Detection}. J. W. C. van Lint, S. P. Hoogendoorn, and H. J. van Zuylen, 
    "Accurate Freeway Travel Time Prediction with State-Space Neural Networks Under Missing Data," 
    \textit{Transportation Research Part C: Emerging Technologies}, vol. 13, no. 5-6, pp. 347-369, Oct.-Dec. 2005. 
    DOI: \url{https://doi.org/10.1016/j.trc.2005.07.001}.
    
    \item \textbf{Edge Computing for Traffic Systems}. Y. Mao, C. You, J. Zhang, K. Huang, and K. B. Letaief, 
    "A Survey on Mobile Edge Computing: The Communication Perspective," 
    \textit{IEEE Communications Surveys \& Tutorials}, vol. 19, no. 4, pp. 2322-2358, 2017. 
    DOI: \url{https://doi.org/10.1109/COMST.2017.2745201}.
    
    \item \textbf{Microservices Architecture}. M. Villamizar, O. Garces, H. Castro, M. Verano, L. Salamanca, R. Casallas, and S. Gil, 
    "Evaluating the Monolithic and the Microservice Architecture Pattern in the Context of Migrating a Critical System," 
    \textit{Proceedings of the 11th Colombian Computing Conference (11CCC)}, 
    Bogotá, Colombia, 2016, pp. 1-8. DOI: \url{https://doi.org/10.1109/ColombianCC.2016.7750795}.
\end{enumerate}

\vspace{0.5cm}
\textbf{Note}: All academic references include DOI links where available. 
For access to full papers, please refer to your institution's library database or the publishers' websites.

