% ============================================
% REFERENCES - Standalone LaTeX Section
% ============================================
% Copy this entire section into your LaTeX document before \end{document}
% Or use \input{REFERENCES.tex} if you have REFERENCES.tex in the same directory

\newpage
\section*{References}
\addcontentsline{toc}{section}{References}

\subsection*{AI and Machine Learning Libraries}

\begin{enumerate}
    \item \textbf{Ultralytics YOLOv8}. \textit{YOLOv8: You Only Look Once Version 8}. 
    Ultralytics, 2023. [Online]. Available: \url{https://github.com/ultralytics/ultralytics}. 
    License: AGPL-3.0. Version: 8.0.196-8.0.200.
    
    \item \textbf{PyTorch}. \textit{PyTorch: An Imperative Style, High-Performance Deep Learning Library}. 
    Facebook AI Research, 2019. [Online]. Available: \url{https://pytorch.org/}. 
    License: BSD-style. Version: 2.1.0-2.2.0.
    
    \item \textbf{TorchVision}. \textit{TorchVision: Datasets, Transforms and Models for Computer Vision}. 
    PyTorch Team, 2023. [Online]. Available: \url{https://github.com/pytorch/vision}. 
    License: BSD-style. Version: 0.16.0.
    
    \item \textbf{OpenCV}. \textit{Open Source Computer Vision Library}. 
    OpenCV Team, 2023. [Online]. Available: \url{https://opencv.org/}. 
    License: Apache 2.0. Version: 4.8.1.78.
    
    \item \textbf{OpenCV Contrib}. \textit{OpenCV Contrib Modules}. 
    OpenCV Team, 2023. [Online]. Available: \url{https://github.com/opencv/opencv_contrib}. 
    License: Apache 2.0. Version: 4.8.1.78.
    
    \item \textbf{CoreML Tools}. \textit{CoreML Tools: Convert and Optimize Machine Learning Models}. 
    Apple Inc., 2023. [Online]. Available: \url{https://github.com/apple/coremltools}. 
    License: BSD-3-Clause. Version: 7.0+.
    
    \item \textbf{ONNX Runtime}. \textit{ONNX Runtime: Cross-Platform Inference and Training Accelerator}. 
    Microsoft, 2023. [Online]. Available: \url{https://onnxruntime.ai/}. 
    License: MIT. Version: 1.16.0+.
    
    \item \textbf{ONNX}. \textit{Open Neural Network Exchange Format}. 
    ONNX Working Group, 2023. [Online]. Available: \url{https://onnx.ai/}. 
    License: Apache 2.0. Version: 1.15.0.
    
    \item \textbf{Deep SORT Realtime}. \textit{Deep SORT: Simple Online and Realtime Tracking}. 
    Community, 2023. [Online]. Available: \url{https://github.com/nwojke/deep_sort}. 
    License: GPL-3.0. Version: 1.3.2.
    
    \item \textbf{FilterPy}. \textit{FilterPy: Kalman Filtering Library for Python}. 
    R. Labbe, 2023. [Online]. Available: \url{https://github.com/rlabbe/filterpy}. 
    License: MIT. Version: 1.4.5.
    
    \item \textbf{scikit-learn}. \textit{Scikit-learn: Machine Learning in Python}. 
    Scikit-learn Developers, 2023. [Online]. Available: \url{https://scikit-learn.org/}. 
    License: BSD-3-Clause. Version: 1.3.0+.
\end{enumerate}

\subsection*{Web Frameworks and APIs}

\begin{enumerate}[resume]
    \item \textbf{FastAPI}. \textit{FastAPI: Modern, Fast Web Framework for Building APIs}. 
    Sebastián Ramírez, 2023. [Online]. Available: \url{https://fastapi.tiangolo.com/}. 
    License: MIT. Version: 0.104.1.
    
    \item \textbf{Uvicorn}. \textit{Uvicorn: Lightning-Fast ASGI Server}. 
    Encode, 2023. [Online]. Available: \url{https://www.uvicorn.org/}. 
    License: BSD. Version: 0.24.0.
    
    \item \textbf{Pydantic}. \textit{Pydantic: Data Validation Using Python Type Annotations}. 
    Samuel Colvin, 2023. [Online]. Available: \url{https://docs.pydantic.dev/}. 
    License: MIT. Version: 2.5.0.
    
    \item \textbf{Pydantic Settings}. \textit{Pydantic Settings: Settings Management Using Pydantic}. 
    Pydantic Team, 2023. [Online]. Available: \url{https://docs.pydantic.dev/latest/usage/settings/}. 
    License: MIT. Version: 2.1.0.
    
    \item \textbf{Python Multipart}. \textit{Python Multipart: Streaming Multipart Parser}. 
    Community, 2023. [Online]. Available: \url{https://github.com/andrew-d/python-multipart}. 
    License: Apache 2.0. Version: 0.0.6.
    
    \item \textbf{aiohttp}. \textit{aiohttp: Async HTTP Client/Server Framework}. 
    aio-libs, 2023. [Online]. Available: \url{https://docs.aiohttp.org/}. 
    License: Apache 2.0. Version: 3.9.1.
    
    \item \textbf{aiofiles}. \textit{aiofiles: Async File I/O}. 
    Tin Tvrtković, 2023. [Online]. Available: \url{https://github.com/Tinche/aiofiles}. 
    License: Apache 2.0. Version: 23.2.1.
\end{enumerate}

\subsection*{Data Processing and Scientific Computing}

\begin{enumerate}[resume]
    \item \textbf{NumPy}. \textit{NumPy: The Fundamental Package for Scientific Computing}. 
    NumPy Developers, 2023. [Online]. Available: \url{https://numpy.org/}. 
    License: BSD-3-Clause. Version: 1.26.2.
    
    \item \textbf{Pandas}. \textit{Pandas: Powerful Data Analysis and Manipulation Library}. 
    Pandas Development Team, 2023. [Online]. Available: \url{https://pandas.pydata.org/}. 
    License: BSD-3-Clause. Version: 2.1.3.
    
    \item \textbf{SciPy}. \textit{SciPy: Fundamental Algorithms for Scientific Computing}. 
    SciPy Developers, 2023. [Online]. Available: \url{https://scipy.org/}. 
    License: BSD-3-Clause. Version: 1.11.4.
    
    \item \textbf{Matplotlib}. \textit{Matplotlib: Visualization with Python}. 
    Matplotlib Development Team, 2023. [Online]. Available: \url{https://matplotlib.org/}. 
    License: PSF-based. Version: 3.7.0+.
    
    \item \textbf{Pillow (PIL)}. \textit{Pillow: Python Imaging Library}. 
    Alex Clark and Contributors, 2023. [Online]. Available: \url{https://pillow.readthedocs.io/}. 
    License: HPND. Version: 10.1.0.
    
    \item \textbf{ImageIO}. \textit{ImageIO: Python Library for Reading and Writing Image Data}. 
    ImageIO Contributors, 2023. [Online]. Available: \url{https://imageio.readthedocs.io/}. 
    License: BSD-2-Clause. Version: 2.31.5.
\end{enumerate}

\subsection*{Databases and Caching}

\begin{enumerate}[resume]
    \item \textbf{PostgreSQL}. \textit{PostgreSQL: Advanced Open Source Relational Database}. 
    PostgreSQL Global Development Group, 2023. [Online]. Available: \url{https://www.postgresql.org/}. 
    License: PostgreSQL License (similar to BSD/MIT). Version: Latest.
    
    \item \textbf{asyncpg}. \textit{asyncpg: Fast PostgreSQL Database Client Library}. 
    MagicStack Inc., 2023. [Online]. Available: \url{https://github.com/MagicStack/asyncpg}. 
    License: Apache 2.0. Version: 0.29.0.
    
    \item \textbf{SQLAlchemy}. \textit{SQLAlchemy: The Python SQL Toolkit and ORM}. 
    SQLAlchemy Authors, 2023. [Online]. Available: \url{https://www.sqlalchemy.org/}. 
    License: MIT. Version: 2.0.23.
    
    \item \textbf{Alembic}. \textit{Alembic: Database Migration Tool for SQLAlchemy}. 
    SQLAlchemy Authors, 2023. [Online]. Available: \url{https://alembic.sqlalchemy.org/}. 
    License: MIT. Version: 1.12.1.
    
    \item \textbf{Redis}. \textit{Redis: In-Memory Data Structure Store}. 
    Redis Ltd., 2023. [Online]. Available: \url{https://redis.io/}. 
    License: BSD-3-Clause. Version: Latest.
    
    \item \textbf{redis-py}. \textit{Redis Python Client}. 
    Redis Ltd., 2023. [Online]. Available: \url{https://github.com/redis/redis-py}. 
    License: MIT. Version: 5.0.1.
    
    \item \textbf{hiredis}. \textit{hiredis: C Parser for Redis Protocol}. 
    Redis Ltd., 2023. [Online]. Available: \url{https://github.com/redis/hiredis-py}. 
    License: BSD-3-Clause. Version: 2.2.3.
\end{enumerate}

\subsection*{Message Queues and Streaming}

\begin{enumerate}[resume]
    \item \textbf{Apache Kafka}. \textit{Apache Kafka: Distributed Event Streaming Platform}. 
    Apache Software Foundation, 2023. [Online]. Available: \url{https://kafka.apache.org/}. 
    License: Apache 2.0. Version: Latest.
    
    \item \textbf{aiokafka}. \textit{aiokafka: Async Kafka Client for Python}. 
    Community, 2023. [Online]. Available: \url{https://github.com/aio-libs/aiokafka}. 
    License: Apache 2.0. Version: 0.8.1-0.9.0.
    
    \item \textbf{Confluent Kafka Python}. \textit{Confluent's Python Client for Apache Kafka}. 
    Confluent Inc., 2023. [Online]. Available: \url{https://github.com/confluentinc/confluent-kafka-python}. 
    License: Apache 2.0. Version: 2.3.0.
    
    \item \textbf{kafka-python}. \textit{Python Client for Apache Kafka}. 
    Community, 2023. [Online]. Available: \url{https://github.com/dpkp/kafka-python}. 
    License: Apache 2.0. Version: 2.0.2.
\end{enumerate}

\subsection*{Monitoring and Observability}

\begin{enumerate}[resume]
    \item \textbf{Prometheus}. \textit{Prometheus: Monitoring and Alerting Toolkit}. 
    Prometheus Authors, 2023. [Online]. Available: \url{https://prometheus.io/}. 
    License: Apache 2.0. Version: Latest.
    
    \item \textbf{prometheus-client}. \textit{Prometheus Python Client Library}. 
    Prometheus Authors, 2023. [Online]. Available: \url{https://github.com/prometheus/client_python}. 
    License: Apache 2.0. Version: 0.19.0.
    
    \item \textbf{Grafana}. \textit{Grafana: Analytics and Monitoring Platform}. 
    Grafana Labs, 2023. [Online]. Available: \url{https://grafana.com/}. 
    License: AGPL-3.0. Version: Latest.
    
    \item \textbf{psutil}. \textit{psutil: Cross-Platform System and Process Utilities}. 
    Giampaolo Rodola, 2023. [Online]. Available: \url{https://github.com/giampaolo/psutil}. 
    License: BSD-3-Clause. Version: 5.9.0+.
    
    \item \textbf{structlog}. \textit{structlog: Structured Logging for Python}. 
    Hynek Schlawack, 2023. [Online]. Available: \url{https://www.structlog.org/}. 
    License: Apache 2.0 / MIT. Version: 23.2.0.
    
    \item \textbf{python-json-logger}. \textit{Python JSON Logger: JSON Formatter for Python Logging}. 
    Community, 2023. [Online]. Available: \url{https://github.com/madzak/python-json-logger}. 
    License: BSD-2-Clause. Version: 2.0.7.
\end{enumerate}

\subsection*{Containerization and Orchestration}

\begin{enumerate}[resume]
    \item \textbf{Docker}. \textit{Docker: Containerization Platform}. 
    Docker Inc., 2023. [Online]. Available: \url{https://www.docker.com/}. 
    License: Apache 2.0 (Community Edition). Version: Latest.
    
    \item \textbf{Docker Compose}. \textit{Docker Compose: Multi-Container Docker Applications}. 
    Docker Inc., 2023. [Online]. Available: \url{https://docs.docker.com/compose/}. 
    License: Apache 2.0. Version: Latest.
    
    \item \textbf{Kubernetes}. \textit{Kubernetes: Container Orchestration Platform}. 
    Cloud Native Computing Foundation, 2023. [Online]. Available: \url{https://kubernetes.io/}. 
    License: Apache 2.0. Version: Latest.
    
    \item \textbf{Helm}. \textit{Helm: The Kubernetes Package Manager}. 
    CNCF, 2023. [Online]. Available: \url{https://helm.sh/}. 
    License: Apache 2.0. Version: Latest.
    
    \item \textbf{Kustomize}. \textit{Kustomize: Kubernetes Native Configuration Management}. 
    Kubernetes SIG CLI, 2023. [Online]. Available: \url{https://kustomize.io/}. 
    License: Apache 2.0. Version: Latest.
\end{enumerate}

\subsection*{Video and Media Processing}

\begin{enumerate}[resume]
    \item \textbf{PyAV}. \textit{PyAV: Pythonic Bindings for FFmpeg}. 
    Community, 2023. [Online]. Available: \url{https://github.com/PyAV-Org/PyAV}. 
    License: BSD-2-Clause. Version: 11.0.0-12.0.0.
    
    \item \textbf{FFmpeg}. \textit{FFmpeg: Multimedia Framework}. 
    FFmpeg Developers, 2023. [Online]. Available: \url{https://ffmpeg.org/}. 
    License: LGPL/GPL. Version: Latest.
    
    \item \textbf{yt-dlp}. \textit{yt-dlp: YouTube Downloader}. 
    Community, 2023. [Online]. Available: \url{https://github.com/yt-dlp/yt-dlp}. 
    License: Unlicense. Version: Latest.
\end{enumerate}

\subsection*{Utilities and Tools}

\begin{enumerate}[resume]
    \item \textbf{Python-dotenv}. \textit{python-dotenv: Load Environment Variables from .env File}. 
    Saurabh Kumar, 2023. [Online]. Available: \url{https://github.com/theskumar/python-dotenv}. 
    License: BSD-3-Clause. Version: 1.0.0.
    
    \item \textbf{PyYAML}. \textit{PyYAML: YAML Parser and Emitter for Python}. 
    Kirill Simonov, 2023. [Online]. Available: \url{https://pyyaml.org/}. 
    License: MIT. Version: 6.0.1.
    
    \item \textbf{pytz}. \textit{pytz: World Timezone Definitions for Python}. 
    Stuart Bishop, 2023. [Online]. Available: \url{https://pythonhosted.org/pytz/}. 
    License: MIT. Version: 2023.3.
    
    \item \textbf{dateutils}. \textit{dateutils: Various Utilities for Working with Dates}. 
    Community, 2023. [Online]. Available: \url{https://github.com/dateutil/dateutil}. 
    License: Apache 2.0 / BSD. Version: 0.6.12.
    
    \item \textbf{PyJWT}. \textit{PyJWT: JSON Web Token Implementation}. 
    José Padilla, 2023. [Online]. Available: \url{https://github.com/jpadilla/pyjwt}. 
    License: MIT. Version: 2.8.0+.
    
    \item \textbf{pyserial}. \textit{pyserial: Serial Port Access Library}. 
    Chris Liechti, 2023. [Online]. Available: \url{https://github.com/pyserial/pyserial}. 
    License: BSD-3-Clause. Version: 3.5.
    
    \item \textbf{httpx}. \textit{httpx: HTTP Client for Python}. 
    Encode, 2023. [Online]. Available: \url{https://www.python-httpx.org/}. 
    License: BSD. Version: 0.25.2.
\end{enumerate}

\subsection*{Testing and Code Quality}

\begin{enumerate}[resume]
    \item \textbf{pytest}. \textit{pytest: Python Testing Framework}. 
    Holger Krekel and Contributors, 2023. [Online]. Available: \url{https://docs.pytest.org/}. 
    License: MIT. Version: 7.4.3.
    
    \item \textbf{pytest-asyncio}. \textit{pytest-asyncio: Pytest Support for asyncio}. 
    Community, 2023. [Online]. Available: \url{https://github.com/pytest-dev/pytest-asyncio}. 
    License: Apache 2.0. Version: 0.21.1.
    
    \item \textbf{pytest-cov}. \textit{pytest-cov: Coverage Plugin for pytest}. 
    Community, 2023. [Online]. Available: \url{https://github.com/pytest-dev/pytest-cov}. 
    License: MIT. Version: 4.1.0.
    
    \item \textbf{Black}. \textit{Black: The Uncompromising Code Formatter}. 
    Łukasz Langa, 2023. [Online]. Available: \url{https://black.readthedocs.io/}. 
    License: MIT. Version: 23.11.0.
    
    \item \textbf{Ruff}. \textit{Ruff: Extremely Fast Python Linter}. 
    Astral Software, 2023. [Online]. Available: \url{https://github.com/astral-sh/ruff}. 
    License: MIT. Version: 0.1.6+.
    
    \item \textbf{mypy}. \textit{mypy: Static Type Checker for Python}. 
    Jukka Lehtosalo, 2023. [Online]. Available: \url{https://mypy.readthedocs.io/}. 
    License: MIT. Version: 1.7.1.
    
    \item \textbf{pre-commit}. \textit{pre-commit: Git Hooks Framework}. 
    Community, 2023. [Online]. Available: \url{https://pre-commit.com/}. 
    License: MIT. Version: 3.5.0.
\end{enumerate}

\subsection*{Protocols and Standards}

\begin{enumerate}[resume]
    \item \textbf{NTCIP}. \textit{National Transportation Communications for ITS Protocol}. 
    NTCIP Joint Committee, 2023. [Online]. Available: \url{https://www.ntcip.org/}. 
    Standard: NTCIP 1202 v03, NTCIP 1201.
    
    \item \textbf{SNMP}. \textit{Simple Network Management Protocol}. 
    IETF, 2023. [Online]. Available: \url{https://www.ietf.org/rfc/rfc1157.txt}. 
    Standard: RFC 1157.
    
    \item \textbf{pysnmp}. \textit{pysnmp: SNMP Library for Python}. 
    Community, 2023. [Online]. Available: \url{https://github.com/etingof/pysnmp}. 
    License: BSD-2-Clause. Version: Latest.
\end{enumerate}

\subsection*{Additional Resources}

\begin{enumerate}[resume]
    \item \textbf{Python}. \textit{Python Programming Language}. 
    Python Software Foundation, 2023. [Online]. Available: \url{https://www.python.org/}. 
    License: PSF License. Version: 3.12+.
    
    \item \textbf{asyncio}. \textit{asyncio: Asynchronous I/O Library}. 
    Python Software Foundation, 2023. [Online]. Available: \url{https://docs.python.org/3/library/asyncio.html}. 
    License: PSF License. Part of Python Standard Library.
    
    \item \textbf{ByteTrack}. \textit{ByteTrack: Multi-Object Tracking by Associating Every Detection Box}. 
    Yifu Zhang et al., 2021. [Online]. Available: \url{https://github.com/ifzhang/ByteTrack}. 
    License: MIT. Implementation: Custom SimpleByteTracker.
    
    \item \textbf{Kalman Filter}. \textit{Kalman Filter: Algorithm for State Estimation}. 
    R. E. Kalman, 1960. "A New Approach to Linear Filtering and Prediction Problems," 
    \textit{Journal of Basic Engineering}, vol. 82, no. 1, pp. 35-45.
\end{enumerate}

\vspace{1cm}
\textbf{Note}: All version numbers and URLs are accurate as of December 2025. 
For the most current information, please refer to the official project repositories and documentation.

